---
title: "Week 13: Communicating results"
author: "John Paul Helveston"
date: April 08, 2020
output:
  xaringan::moon_reader:
    css: ['default', 'https://emse-eda-gwu.github.io/2020-Spring/classNotes/classNotes.css']
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      beforeInit: "https://platform.twitter.com/widgets.js"
    seal: false
---

```{r setup, include=FALSE}
library(here)
source(here('setup.R'))
```

name: xaringan-title
class: title-slide, center, middle, inverse

# Week 13: Communicating results

.large[EMSE 4197 | John Paul Helveston | April 08, 2020]

```{r child = here('parts', 'intro.Rmd')}
```
---
class: inverse, middle

# Communicating results

## 1. Telling a story
## 2. Designing slides
## 3. Giving a talk

---
class: inverse, middle

# Communicating results

## 1. .orange[Telling a story]
## 2. Designing slides
## 3. Giving a talk

```{r child = here('parts', 'telling_story.Rmd')}
```

---
class: inverse, middle

# Communicating results

## 1. Telling a story
## 2. .orange[Designing slides]
## 3. Giving a talk

```{r child = here('parts', 'designing_slides.Rmd')}
```

---
class: inverse, middle

# Communicating results

## 1. Telling a story
## 2. Designing slides
## 3. .orange[Giving a talk]

```{r child = here('parts', 'giving_a_talk.Rmd')}
```
