---
title: "Course Schedule"
output:
  html_document:
    number_sections: false
    toc: no
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
rm(list=objects()) # start with a clean workspace
source("knitr_setup.R")
```

Here's your roadmap for the semester!

Readings legend:

- Healy == Healy, Kieran. "Data Visualization: A practical introduction" [[free online](http://socviz.co/)], [[buy on amazon](https://www.amazon.com/Data-Visualization-Introduction-Kieran-Healy/dp/0691181624)]
- R4DS == Grolemund, Garrett and Wickham, Hadley. "R for Data Science" [[free online](https://r4ds.had.co.nz/)], [[buy on amazon](https://www.amazon.com/Data-Science-Transform-Visualize-Model/dp/1491910399)]
- Wilke == Wilke, Claus O. "Fundamentals of Data Visualization" [[free online](https://serialmentor.com/dataviz/)], [[buy on amazon](https://www.amazon.com/Fundamentals-Data-Visualization-Informative-Compelling/dp/1492031089)]





```{r echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(here)
library(gsheet)
options(knitr.kable.NA = '')
schedule <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1GkCv6FGzn7kNU4yC5QyCVAt2OnfS3yK1UVNeG2u0z4g/edit?usp=sharing')
# Define the first and last of class and finals start date
start  <- as.Date("2020/01/13")
end    <- as.Date("2020/04/27")
makeup <- as.Date("2020/04/28")
finals <- as.Date("2020/05/04")
# Format the dates
dates <- format(seq(start, end, by = "week"), format="%m/%d")
dates <- c(dates, format(c(makeup, finals), format="%m/%d"))
# Make the schedule data frame
schedule$Date <- dates
# Define the week
schedule$Week <- c(seq(1:(length(dates)-1)), (length(dates)-1))
schedule <- schedule[c('Week', 'Date', 'Topics', 'Class Notes', 'Readings', 'Assignments')]
# Render the schedule as markdown
kable(schedule, format='markdown')
```
NOTE: In accordance with university policy, the final exam will be given during the final exam period and not the last week of the semester.

