
---
class: middle, inverse, center

# Ask and you shall [receive](https://github.com/thomasp85/gganimate/issues/372)

---
class: inverse

# R tip of the week:

## Copy-paste magic with [`datapasta`](https://github.com/MilesMcBain/datapasta)

<br>

### **Useful for "small data"**: e.g., [U.S. State Abbreviations](https://www.50states.com/abbreviations.htm)

---
## Today's data

"Clean" data
```{r, eval=FALSE}
wildlife_impacts <- read_csv(here::here('data', 'wildlife_impacts.csv'))
milk_production  <- read_csv(here::here('data', 'milk_production.csv'))
msleep           <- read_csv(here::here('data', 'msleep.csv'))
```

"Messy" data
```{r, eval=FALSE}
wind     <- read_excel(here::here('data', 'US_State_Wind_Energy_Facts_2018.xlsx'))
hot_dogs <- read_excel(here::here('data', 'hot_dog_winners.xlsx'))
pc_sales <- read_excel(here::here('data', 'pc_sales_2018.xlsx'), skip = 5)
weather  <- readRDS(here::here('data', 'weather.Rds'))
```

## Plus two new packages:

- **janitor**: for cleaning names
- **lubridate**: for manipulating dates

---
# One more note

`here()` != `here::here()`

---
# One more note

`here()` != `here::here()`

<br>

Syntax:

`library` + `::` + `function`

---
# One more note

.leftcol[
`here()` != `here::here()`

<br>

Syntax:

`library` + `::` + `function`

<br>
]
.rightcol[
Example:

```{r, eval=FALSE}
milk_production %>%
    filter(year == 2000)
```

```{r, eval=FALSE}
milk_production %>%
    dplyr::filter(year == 2000) #<<
```
]
