---
title: "Week 11 In Class Notes"
output:
    html_document:
        theme: lumen
        highlight: tango
---

Load libraries and settings
```{r setup, message=FALSE, warning=FALSE}
# install.packages('HistData')
# install.packages('GGally')

library(HistData)
library(GGally)
library(knitr)
library(cowplot)
library(tidyverse)
library(here)
options(
    htmltools.dir.version = FALSE,
    knitr.table.format = "html",
    knitr.kable.NA = '',
    tibble.width = Inf)
knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.retina = 3)
dplyr.width = Inf
```

Load all the data sets:

```{r}
wildlife_impacts <- read_csv(here::here('data', 'wildlife_impacts.csv'))
msleep           <- read_csv(here::here('data', 'msleep.csv'))
```

# 1. Correlation

Using the `wildlife_impacts` data frame:

1. Find the two variables with the largest correlation in absolute value <br>(i.e. closest to -1 or 1).
2. Create a scatter plot of those two variables. Include an annotation for the Pearson correlation coefficient.

```{r}

# Write code to find the two most correlated variables

```

```{r}

# Write code to visualize the two most correlated variables

```

# 2. Linear models

Using the `msleep` data frame:

1. Create a scatter plot of `brainwt` versus `bodywt`.
2. Include an annotation for the Pearson correlation coefficient.
3. Include an annotation for the best fit line.

Bonus: Compare your results to a log-linear relationship by converting the x and y variables to the log of x and y.

```{r}

# Write code to visualize the brainwt and bodywt variables

```
