---
title: "Week 11: Correlation Analysis"
author: "John Paul Helveston"
date: March 25, 2020
output:
  xaringan::moon_reader:
    css: ['default', 'https://emse-eda-gwu.github.io/2020-Spring/classNotes/classNotes.css']
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      beforeInit: "https://platform.twitter.com/widgets.js"
    seal: false
---

```{r setup, include=FALSE}
source('setup.R')
```

name: xaringan-title
class: title-slide, center, middle, inverse

# Week 11: Correlation Analysis

.large[EMSE 4197 | John Paul Helveston | March 25, 2020]

```{r child = here('parts', 'intro.Rmd')}
```

---
class: inverse, middle

# Correlation Analysis

## 1. What is correlation?
## 2. Visualizing correlation
## 3. Linear models 
## 4. Visualizing linear models 

---
class: inverse, middle

# Correlation Analysis

## 1. .orange[What is correlation?]
## 2. Visualizing correlation
## 3. Linear models 
## 4. Visualizing linear models 

```{r child = here('parts', 'correlation.Rmd')}
```

---
class: inverse, middle

# Correlation Analysis

## 1. What is correlation?
## 2. .orange[Visualizing correlation]
## 3. Linear models
## 4. Visualizing linear models 

```{r child = here('parts', 'correlation_viz.Rmd')}
```

---
class: inverse, middle

# Correlation Analysis

## 1. What is correlation?
## 2. Visualizing correlation
## 3. .orange[Linear models]
## 4. Visualizing linear models 

```{r child = here('parts', 'regression.Rmd')}
```

---
class: inverse, middle

# Correlation Analysis

## 1. What is correlation?
## 2. Visualizing correlation
## 3. Linear models
## 4. .orange[Visualizing linear models]

```{r child = here('parts', 'regression_viz.Rmd')}
```
