---
title: "Assignment 7: Hockey Trends Redesign"
author: First Last
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
    warning    = FALSE,
    message    = FALSE,
    fig.align  = "center")
library(tidyverse)
library(readxl)
library(here)
library(cowplot)
library(readxl)
library(janitor)
options(dplyr.width = Inf)
```

# Clean the data

```{r}

# Write code here

```

Write a few sentences here describing any modifications you made to the original data and why you did it.

# Create new variables

```{r}

# Write code here

```

# Summarize the data

```{r}

# Write code here

```

Write a few sentences explaining your summary measures and what you learned from them.

# Data visualization 1

```{r}

# Write code here

```

# Data visualization 2

```{r}

# Write code here

```

# Summary of analysis

Write a summary of your analysis. I'm specifically looking for a discussion of the following:

    - What was wrong with the original chart? Discuss specific design principles we have covered in class.
    - Discuss the message you intended to convey with each of your charts and how your design choices draw attention to that message.
