
---
class: inverse, middle

# Topics

## 1. Making a (good) ggplot
## 2. .orange[Using facets]
## 3. Manipulating factors
## 4. Graphing proportions

---
class: center, middle

## When # of categories is large, consider facets

.leftcol[
```{r diamonds_bars_stacked, echo=FALSE, fig.height=6}
ggplot(diamonds, aes(clarity, fill=cut, group=cut)) +
    geom_bar(stat="count", position="stack") +
    scale_y_continuous(expand = expand_scale(mult = c(0, 0.05))) +
    theme_minimal_hgrid()
```
]
.rightcol[
```{r diamonds_bars_dodged, echo=FALSE, fig.height=6}
ggplot(diamonds, aes(clarity, fill=cut, group=cut)) +
    geom_bar(stat="count", position="dodge") +
    scale_y_continuous(expand = expand_scale(mult = c(0, 0.05))) +
    theme_minimal_hgrid()
```
]

---
## When # of categories is large, consider facets

.leftcol60[
```{r}
diamonds_summary <- diamonds %>%
  count(clarity, cut)
```
```{r diamonds_facet, fig.show='hide'}
ggplot(diamonds_summary) +
  geom_col(aes(x = clarity, y = n)) +
  facet_wrap(~cut, nrow = 1) + #<<
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  theme_minimal_hgrid()
```
]

```{r ref.label='diamonds_facet', echo=FALSE, fig.height=3, fig.width=15}
```

---
.leftcol[.code70[
## When # of categories is large, consider facets

```{r}
diamonds_summary <- diamonds %>%
  count(clarity, cut)
```
```{r diamonds_facet_ncol, fig.show='hide'}
ggplot(diamonds_summary) +
  geom_col(aes(x = clarity, y = n)) +
  facet_wrap(~cut, ncol = 2) + #<<
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  theme_minimal_hgrid()
```
]]
.rightcol[
```{r ref.label='diamonds_facet_ncol', echo=FALSE, fig.height=8, fig.width=8, fig.align='center'}
```
]

---
class: inverse

.leftcol60[
## Your turn

Create the following charts. For this exercise, you can remove `NA` values.

**Hint**: You may need to reshape and / or summarize the data before plotting!

Data: `lotr_words.csv`
```{r, echo=FALSE, fig.width=7, fig.height=5}
lotr_summary <- lotr_words %>%
  gather(key = 'gender', value = 'wordCount',
         Female:Male)

ggplot(lotr_summary) +
  geom_col(aes(x = Film, y = wordCount, fill = gender)) +
  facet_wrap(~Race, ncol = 1) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid() +
  labs(
    x = 'Word count',
    y = 'Film',
    fill = 'Gender')
```
]
.rightcol40[

Data: `wildlife_impacts.csv`
```{r, echo=FALSE, fig.width=5, fig.height=8}
wildlife_summary <- wildlife_impacts %>%
  filter(!is.na(time_of_day)) %>%
  count(operator, time_of_day) %>%
  mutate(
    operator = str_to_title(operator),
    operator = fct_reorder(operator, n),
    time_of_day = fct_rev(fct_reorder(time_of_day, n)))

ggplot(wildlife_summary) +
  geom_col(aes(x = operator, y = n)) +
  facet_wrap(~time_of_day, ncol = 1) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid() +
  labs(
    x = 'Airline',
    y = 'Number of incidents')
```
]
