
---
class: inverse, middle

# Topics

## 1. Making a (good) ggplot
## 2. Using facets
## 3. .orange[Manipulating factors]
## 4. Graphing proportions

---
class: inverse

# Common situations:

### 1. What if the factor order doesn't follow another variable?
### 2. What if the factors are too long?
### 3. What if there are too many levels?

---
### 1. What if the factor order doesn't follow another variable?

.leftcol[.code70[
```{r}
lotr_long <- lotr_words %>%
  gather(key = 'gender', value = 'wordCount',
         Female:Male)
```
```{r lotr_bars, fig.show='hide'}
ggplot(lotr_long) +
  geom_col(aes(x = Film, y = wordCount),
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid()
```
]]
.rightcol[
```{r ref.label='lotr_bars', echo=FALSE, fig.height=4, fig.width=7, fig.align='center'}
```
]

---
### 1. What if the factor order doesn't follow another variable?

.leftcol[.code70[

Use `fct_relevel()` to manually change the order

```{r}
lotr_long <- lotr_words %>%
  gather(key = 'gender', value = 'wordCount',
         Female:Male) %>%
  mutate( #<<
    Film = fct_relevel(Film, levels = c( #<<
      'The Fellowship Of The Ring', #<<
      'The Two Towers', #<<
      'The Return Of The King'))) #<<
```
```{r lotr_bars_relevel, fig.show='hide'}
ggplot(lotr_long) +
  geom_col(aes(x = Film, y = wordCount),
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid()
```
]]
.rightcol[
```{r ref.label='lotr_bars_relevel', echo=FALSE, fig.height=4, fig.width=7, fig.align='center'}
```
]

---
### 2. What if the factors are too long?

.leftcol[.code70[

```{r}
lotr_long <- lotr_words %>%
  gather(key = 'gender', value = 'wordCount',
         Female:Male)
```
```{r, eval=FALSE}
ggplot(lotr_long) +
  geom_col(aes(x = Film, y = wordCount),
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid()
```
]]
.rightcol[
```{r ref.label='lotr_bars', echo=FALSE, fig.height=4, fig.width=7, fig.align='center'}
```
]

---
### 2. What if the factors are too long?

.leftcol55[.code60[

Use `fct_recode()` to manually change the levels

```{r}
lotr_long <- lotr_words %>%
  gather(key = 'gender', value = 'wordCount',
         Female:Male) %>%
  mutate( #<<
    Film = fct_recode(Film, #<<
      'The Fellowship\nof the Ring' = 'The Fellowship Of The Ring', #<<
      'The Return\nof the King' = 'The Return Of The King'))  #<<
```
```{r lotr_bars_recode, fig.show='hide'}
ggplot(lotr_long) +
  geom_col(aes(x = Film, y = wordCount),
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid()
```
]]
.rightcol45[
```{r ref.label='lotr_bars_recode', echo=FALSE, fig.height=4, fig.width=7, fig.align='center'}
```
]

---
### 2. What if the factors are too long?

.leftcol55[.code60[

Use `fct_recode()` to manually change the levels

...and don't forget to also update the order

```{r}
lotr_long <- lotr_words %>%
  gather(key = 'gender', value = 'wordCount',
         Female:Male) %>%
  mutate(
    Film = fct_recode(Film,
      'The Fellowship\nof the Ring' = 'The Fellowship Of The Ring',
      'The Return\nof the King' = 'The Return Of The King'),
    Film = fct_relevel(Film,  c( #<<
      'The Fellowship\nof the Ring', 'The Two Towers', #<<
      'The Return\nof the King')))  #<<
```
```{r lotr_bars_recode_reorder, fig.show='hide'}
ggplot(lotr_long) +
  geom_col(aes(x = Film, y = wordCount),
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid()
```
]]
.rightcol45[
```{r ref.label='lotr_bars_recode_reorder', echo=FALSE, fig.height=4, fig.width=7, fig.align='center'}
```
]

---
### 3. What if there are too many levels?

.leftcol55[.code70[
```{r}
federal_spending_summary <- federal_spending %>%
  group_by(department) %>%
  summarise(rd_budget = sum(rd_budget)) %>%
  mutate(
    department = fct_reorder(department, rd_budget))
```
```{r federal_spending, fig.show='hide'}
ggplot(federal_spending_summary) +
  geom_col(aes(x = department, y = rd_budget),
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid()
```
]]
.rightcol45[
```{r ref.label='federal_spending', echo=FALSE, fig.height=8, fig.width=8}
```
]

---

### 3. What if there are too many levels?

.leftcol55[.code70[

Keep top N, use `fct_other()` to merge rest into "Other"

```{r}
federal_spending_summary <- federal_spending %>%
  mutate( #<<
    department = fct_other(department, #<<
      keep = c('DOD', 'HHS', 'NIH', 'NASA', 'DOE'))) %>% #<<
  group_by(department) %>%
  summarise(rd_budget = sum(rd_budget)) %>%
  mutate(
    department = fct_reorder(department, rd_budget))
```
```{r federal_spending_top5, fig.show='hide'}
ggplot(federal_spending_summary) +
  geom_col(aes(x = department, y = rd_budget),
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid()
```
]]
.rightcol45[
```{r ref.label='federal_spending_top5', echo=FALSE, fig.height=6, fig.width=8}
```
]

---
### 3. What if there are _really_ too many levels?

.leftcol[.code70[

```{r}
avengers <- avengers %>%
  mutate(name_alias =
         fct_reorder(name_alias, appearances))
```
```{r avengers_bar, fig.show='hide'}
ggplot(avengers) +
  geom_col(aes(x = name_alias, y = appearances),
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid()
```
]]
.rightcol[
```{r ref.label='avengers_bar', echo=FALSE, fig.height=8, fig.width=8}
```
]

---
### 3. What if there are _really_ too many levels?

.leftcol[.code70[

Keep top N, drop the rest

```{r}
avengers_top10 <- avengers %>%
  mutate(name_alias =
         fct_reorder(name_alias, appearances)) %>%
  arrange(desc(appearances)) %>% #<<
  slice(1:10) #<<
```
```{r avengers_top10, fig.show='hide'}
ggplot(avengers_top10) +
  geom_col(aes(x = name_alias, y = appearances),
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid()
```
]]
.rightcol[
```{r ref.label='avengers_top10', echo=FALSE, fig.height=8, fig.width=8}
```
]

---
### 3. What if there are _really_ too many levels?

.leftcol[.code70[

Keep top N, drop the rest

```{r}
avengers_top10 <- avengers %>%
  mutate(name_alias =
         fct_reorder(name_alias, appearances)) %>%
  arrange(desc(appearances)) %>%
  group_by(gender) %>% #<<
  slice(1:10)
```
```{r avengers_top10_gender, fig.show='hide'}
ggplot(avengers_top10) +
  geom_col(aes(x = name_alias, y = appearances,
               fill = gender), #<<
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid() +
  labs('Top 10 male and female avengers\nin order of appearances')
```
]]
.rightcol[
```{r ref.label='avengers_top10_gender', echo=FALSE, fig.height=8, fig.width=8}
```
]

---
### 3. What if there are _really_ too many levels?

.leftcol[.code70[

Keep top N, drop the rest

```{r}
avengers_top10 <- avengers %>%
  mutate(name_alias =
         fct_reorder(name_alias, appearances)) %>%
  arrange(desc(appearances)) %>%
  group_by(gender) %>%
  slice(1:10)
```
```{r avengers_top10_gender_facet, fig.show='hide'}
ggplot(avengers_top10) +
  geom_col(aes(x = name_alias, y = appearances),
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  facet_wrap(~gender, ncol = 1, #<<
             scales = 'free_y', #<<
             strip.position = 'right') + #<<
  coord_flip() +
  theme_minimal_vgrid()
```
]]
.rightcol[
```{r ref.label='avengers_top10_gender_facet', echo=FALSE, fig.height=8, fig.width=8}
```
]

---
class: inverse

.leftcol[
## Your turn

Use the `milk_production.csv` data to create the following plots

```{r milk_state_summary, echo=FALSE, fig.width=10, fig.height=8}
milk_state_summary <- milk_production %>%
  group_by(state) %>%
  summarise(milk_produced = sum(milk_produced)) %>%
  mutate(state = fct_reorder(state, milk_produced))

ggplot(milk_state_summary) +
  geom_col(aes(x = state, y = milk_produced),
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid() +
  labs(title = 'Total milk production (in lbs) by U.S. state (1970 - 2017)')
```
]
.rightcol[
<br>

**Hint**: You'll need to use `summarise()` to get the total milk production for each state between 1970 - 2017

```{r milk_top10, echo=FALSE, fig.width=8, fig.height=6.5}
milk_top10 <- milk_state_summary %>%
  arrange(desc(milk_produced)) %>%
  slice(1:10)

ggplot(milk_top10) +
  geom_col(aes(x = state, y = milk_produced),
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid() +
  labs(title = 'Milk production (in lbs) of top 10 U.S. states (1970 - 2017)')
```
]
