
---
class: inverse, middle

# Topics

## 1. .orange[Making a (good) ggplot]
## 2. Using facets
## 3. Manipulating factors
## 4. Graphing proportions

---
.leftcol[
## Making a (good) ggplot

1. Format data frame
2. Add main geoms
3. (Flip coordinate)
4. (Reorder factors)
5. Adjust scales
6. Adjust theme
7. Annotate

]
.rightcol[
Before:
```{r birds_before, echo=FALSE, fig.height=3.5, fig.width=4}
wildlife_summary <- wildlife_impacts %>%
  count(operator)

ggplot(wildlife_summary) +
  geom_col(aes(x = operator, y = n),
           width = 0.7, alpha = 0.8)
```

After:
```{r birds_after, echo=FALSE, fig.height=3.5}
wildlife_summary <- wildlife_impacts %>%
  count(operator) %>%
  mutate(
    operator = fct_reorder(operator, n))

ggplot(wildlife_summary) +
  geom_col(aes(x = operator, y = n),
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid() +
  labs(
    x = 'Airline',
    y = 'Count' )
```

]

---
## 1) Format data frame + 2) add main geoms

.leftcol[.code70[

Method 1: Use `geom_bar()`

```{r birds_geom_bar, fig.show='hide'}
ggplot(wildlife_impacts) + #<<
  geom_bar(aes(x = operator), #<<
           width = 0.7, alpha = 0.8)
```
]]
.rightcol[
```{r ref.label='birds_geom_bar', echo=FALSE, fig.height=5, fig.width=5, fig.align='center'}
```
]

---
## 1) Format data frame + 2) add main geoms

.leftcol[.code70[

Method 2: Summarize the data first

```{r}
wildlife_summary <- wildlife_impacts %>%
  count(operator)

wildlife_summary
```

...then use `geom_col()`

```{r birds_geom_col, fig.show='hide'}
ggplot(wildlife_summary) +
  geom_col(aes(x = operator, y = n), #<<
           width = 0.7, alpha = 0.8)
```
]]
.rightcol[
```{r ref.label='birds_geom_col', echo=FALSE, fig.height=5, fig.width=5, fig.align='center'}
```
]

---
## 3) Flip coordinates

.leftcol[.code70[
```{r, eval=FALSE}
wildlife_summary <- wildlife_impacts %>%
  count(operator)
```
```{r birds_coord_flip, fig.show='hide'}
ggplot(wildlife_summary) +
  geom_col(aes(x = operator, y = n),
           width = 0.7, alpha = 0.8) +
  coord_flip() #<<
```
]]
.rightcol[
```{r ref.label='birds_coord_flip', echo=FALSE, fig.height=4, fig.width=6, fig.align='center'}
```
]

---
## 4) Reorder factors with `fct_reorder()`

.leftcol[.code70[
```{r}
wildlife_summary <- wildlife_impacts %>%
  count(operator) %>%
  mutate( #<<
    operator = fct_reorder(operator, n)) #<<
```
```{r birds_fct_reorder, fig.show='hide'}
ggplot(wildlife_summary) +
  geom_col(aes(x = operator, y = n),
           width = 0.7, alpha = 0.8) +
  coord_flip()
```
]]
.rightcol[
```{r ref.label='birds_fct_reorder', echo=FALSE, fig.height=4, fig.width=6.5, fig.align='center'}
```
]

---
## 5) Adjust scales

.leftcol[.code70[

```{r, eval=FALSE}
wildlife_summary <- wildlife_impacts %>%
  count(operator) %>%
  mutate(
    operator = fct_reorder(operator, n))
```

Set y axis limit to 0
```{r birds_scales1, fig.show='hide'}
ggplot(wildlife_summary) +
  geom_col(aes(x = operator, y = n),
           width = 0.7, alpha = 0.8) +
  coord_flip() +
  scale_y_continuous( #<<
    expand = expand_scale(mult = c(0, 0.05))) #<<
```
]]
.rightcol[
```{r ref.label='birds_scales1', echo=FALSE, fig.height=4, fig.width=6.5, fig.align='center'}
```
]

---
## 5) Adjust scales

.leftcol[.code70[

```{r, eval=FALSE}
wildlife_summary <- wildlife_impacts %>%
  count(operator) %>%
  mutate(
    operator = fct_reorder(operator, n))
```

Customize y-axis break points
```{r birds_scales2, fig.show='hide'}
ggplot(wildlife_summary) +
  geom_col(aes(x = operator, y = n),
           width = 0.7, alpha = 0.8) +
  coord_flip() +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05)),
    breaks = c(0, 10000, 20000), #<<
    limits = c(0, 20000)) #<<
```
]]
.rightcol[
```{r ref.label='birds_scales2', echo=FALSE, fig.height=4, fig.width=6.5, fig.align='center'}
```
]

---
## 6) Adjust theme

<br>

### 4 `cowplot` themes you should know

```{r, echo=FALSE, fig.width=15, fig.height=4}
df <- data.frame(x = seq(5), y = seq(5))
half_open <- ggplot(df, aes(x = x, y = y)) +
  theme_half_open() +
  labs(title = "theme_half_open()")
minimal_grid <- ggplot(df, aes(x = x, y = y)) +
  theme_minimal_grid() +
  labs(title = "theme_minimal_grid()")
minimal_vgrid <- ggplot(df, aes(x = x, y = y)) +
  scale_x_continuous(expand = expand_scale(mult = c(0, 0.05))) +
  theme_minimal_vgrid() +
  labs(title = "theme_minimal_vgrid()")
minimal_hgrid <- ggplot(df, aes(x = x, y = y)) +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05))) +
  theme_minimal_hgrid() +
  labs(title = "theme_minimal_hgrid()")
plot_grid(half_open, minimal_grid, minimal_hgrid, minimal_vgrid, nrow=1)
```

---
## 6) Adjust theme

.leftcol[.code70[

For horizontal bars, add only vertical grid

```{r, eval=FALSE}
wildlife_summary <- wildlife_impacts %>%
  count(operator) %>%
  mutate(
    operator = fct_reorder(operator, n))
```
```{r birds_theme, fig.show='hide'}
library(cowplot) #<<

ggplot(wildlife_summary) +
  geom_col(aes(x = operator, y = n),
           width = 0.7, alpha = 0.8) +
  coord_flip() +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  theme_minimal_vgrid() #<<
```
]]
.rightcol[

`theme_minimal_vgrid()`

```{r ref.label='birds_theme', echo=FALSE, fig.height=4, fig.width=6.5, fig.align='center'}
```
]

---
## 7) Annotate

.leftcol[.code70[
```{r, eval=FALSE}
wildlife_summary <- wildlife_impacts %>%
  count(operator) %>%
  mutate(
    operator = fct_reorder(operator, n))
```
```{r birds_annotate, fig.show='hide'}
ggplot(wildlife_summary) +
  geom_col(aes(x = operator, y = n),
           width = 0.7, alpha = 0.8) +
  coord_flip() +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  theme_minimal_vgrid() +
  labs( #<<
    x = 'Airline', #<<
    y = 'Count' ) #<<
```
]]
.rightcol[
```{r ref.label='birds_annotate', echo=FALSE, fig.height=4, fig.width=6.5, fig.align='center'}
```
]

---
## 7) Annotate - Can also just remove y axis

.leftcol[.code70[
```{r, eval=FALSE}
wildlife_summary <- wildlife_impacts %>%
  count(operator) %>%
  mutate(
    operator = fct_reorder(operator, n))
```
```{r birds_annotate_noaxis, fig.show='hide'}
ggplot(wildlife_summary) +
  geom_col(aes(x = operator, y = n),
           width = 0.7, alpha = 0.8) +
  geom_text(aes(x = operator, y = n, label = n), #<<
            hjust = 1, color = 'white', #<<
            nudge_y = -500, size = 7) + #<<
  coord_flip() +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  theme_minimal_vgrid() +
  theme( #<<
    line = element_blank(), #<<
    axis.title.x = element_blank(), #<<
    axis.text.x = element_blank()) + #<<
  labs(
    x = 'Airline',
    y = 'Count' )
```
]]
.rightcol[
```{r ref.label='birds_annotate_noaxis', echo=FALSE, fig.height=4, fig.width=6.5, fig.align='center'}
```
]

---
### Making a (good) ggplot

.leftcol60[.code60[

Data frame:
```{r eval=FALSE}
wildlife_summary <- wildlife_impacts %>%         # 1. Format data frame
  count(operator) %>%
  mutate(
    operator = fct_reorder(operator, n))         # 4. (Reorder factors)
```
Plot:
```{r eval=FALSE}
ggplot(wildlife_summary) +                       # 2. Add main geoms
  geom_col(aes(x = operator, y = n),
           width = 0.7, alpha = 0.8) +
```
```{r eval=FALSE}
  coord_flip() +                                 # 3. (Flip coordinates)
```
```{r eval=FALSE}
  scale_y_continuous(                            # 5. Adjust scales
    expand = expand_scale(mult = c(0, 0.05))) +
```
```{r eval=FALSE}
  theme_minimal_vgrid() +                        # 6. Adjust theme
```
```{r eval=FALSE}
  labs(                                          # 7. Annotate
    x = 'Airline',
    y = 'Count' )
```
]]
.rightcol40[
Final product

```{r ref.label='birds_after', echo=FALSE, fig.height=4, fig.align='center'}
```
]

---
class: inverse

## Your turn

.leftcol40[
Use the `college_all_ages.csv` data to create the following plot

**Hint**: You'll need to compute the median income for each category of major

Making a (good) ggplot:

1. Format data frame
2. Add main geoms
3. (Flip coordinate)
4. (Reorder factors)
5. Adjust scales
6. Adjust theme
7. Annotate

]
.rightcol60[
```{r college_bars, echo=FALSE, fig.width=10}
college_major_summary <- college_all_ages %>%
  group_by(major_category) %>%
  summarise(category_median = median(median)) %>%
  mutate(major_category = fct_reorder(major_category, category_median))

ggplot(college_major_summary) +
  geom_col(aes(x = major_category, y = category_median),
           width = 0.7, alpha = 0.8) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  coord_flip() +
  theme_minimal_vgrid() +
  labs(
    x = 'Category of college major',
    y = 'Median income')
```
]
