<!-- Comparing distributions

- Box plots
- Transparent histograms & densities (good for maybe 2 categories)
- Ridgeline plots (good for lots of categories)

Ridgeline plots: https://wilkelab.org/ggridges/ -->

<!-- Helpful:
https://datavizf17.classes.andrewheiss.com/files/example_2017-09-19.Rmd -->

---
class: center
## Overlapping histograms have issues

```{r marathon_histogram_overlap, fig.show='hide', echo=FALSE}
ggplot(marathon) +
  geom_histogram(aes(x = Age, fill = `M/F`),
                 alpha = 0.7, color = 'white',
                 position = 'identity') +
  scale_fill_manual(values = c('sienna', 'steelblue')) +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05))) +
  theme_minimal_hgrid()
```
```{r marathon_density_overlap, fig.show='hide', echo=FALSE}
ggplot(marathon, aes(x = Age, y = ..count..)) +
  geom_density(aes(fill = `M/F`), alpha = 0.7) +
  scale_fill_manual(values = c('sienna', 'steelblue')) +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05))) +
  theme_minimal_hgrid()
```

.leftcol[
### Bad

```{r ref.label='marathon_histogram_overlap', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]
--
.rightcol[
### Slightly better

```{r ref.label='marathon_density_overlap', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]

---
class: center

## Good when # categories **small**

```{r marathon_density_facet, fig.show='hide', echo=FALSE}
base <- ggplot(marathon, aes(x = Age, y = ..count..)) +
  geom_density(fill = 'grey', alpha = 0.7) +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.05))) +
  theme_minimal_hgrid()

male <- base +
  geom_density(data = marathon %>% filter(`M/F` == 'M'),
               aes(fill = `M/F`), alpha = 0.7) +
  scale_fill_manual(values = 'steelblue') +
  theme(legend.position = 'none')

female <- base +
  geom_density(data = marathon %>% filter(`M/F` == 'F'),
               aes(fill = `M/F`), alpha = 0.7) +
  scale_fill_manual(values = 'sienna') +
  theme(legend.position = 'none')

plot_grid(male, female, labels = c('Male', 'Female'))
```

```{r marathon_diverging_histograms, fig.show='hide', echo=FALSE}
ggplot(marathon, aes(x = Age)) +
    # Add histogram for Female runners:
    geom_histogram(data = marathon %>%
                       filter(`M/F` == 'F'),
                   aes(fill = `M/F`, y=..count..),
                   alpha = 0.7, color = 'white') +
    # Add negative histogram for Male runners:
    geom_histogram(data = marathon %>%
                       filter(`M/F` == 'M'),
                   aes(fill = `M/F`, y=..count..*(-1)),
                   alpha = 0.7, color = 'white') +
    scale_fill_manual(values = c('sienna', 'steelblue')) +
    coord_flip() +
    theme_minimal_hgrid() +
    labs(fill = 'Gender',
         y = 'Count')
```

.leftcol[
### Density facets

```{r ref.label='marathon_density_facet', echo=FALSE, fig.height=3, fig.width=7, fig.align='center'}
```
]
--
.rightcol[
### Diverging histograms

```{r ref.label='marathon_diverging_histograms', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]

---
class: center

## Good when # categories **large**

```{r college_boxplot, fig.show='hide', echo=FALSE}
college_summary <- college_all_ages %>%
    mutate(
        major_category = fct_reorder(major_category, median))

ggplot(college_summary) +
    geom_boxplot(aes(x = major_category, y = median)) +
    coord_flip() +
    theme_minimal_vgrid() +
    labs(x = 'Major category',
         y = 'Median income ($)')
```
```{r college_ridgeplot, fig.show='hide', echo=FALSE}
ggplot(college_summary) +
  geom_density_ridges(aes(x = median, y = major_category),
                      scale = 4, alpha = 0.7) +
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_continuous(expand = c(0, 0)) +
  coord_cartesian(clip = "off") +
  theme_ridges() +
  labs(x = 'Median income ($)',
       y = 'Major category')
```

.leftcol[
### Boxplot

```{r ref.label='college_boxplot', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]
--
.rightcol[
### Ridgeplot

```{r ref.label='college_ridgeplot', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]

---
.leftcol[.code70[
## How to make density facets

You can use `facet_wrap()`,<br>but you won't get the full density overlay
```{r density_facet_nofull, fig.show='hide'}
ggplot(marathon,
       aes(x = Age, y = ..count.., fill = `M/F`)) +
    geom_density(alpha = 0.7) + #<<
    facet_wrap(~`M/F`) + #<<
    scale_fill_manual(
        values = c('sienna', 'steelblue')) +
    scale_y_continuous(
        expand = expand_scale(mult = c(0, 0.05))) +
    theme_minimal_hgrid()
```
]]
.rightcol[
```{r ref.label='density_facet_nofull', echo=FALSE, fig.height=3, fig.width=7, fig.align='center'}
```
]
--
.rightcol[
.center[If you want the full density overlay,<br>you have to hand-make the facets]
```{r ref.label='marathon_density_facet', echo=FALSE, fig.height=3, fig.width=7, fig.align='center'}
```
]

---
## How to make density facets

.leftcol[.code70[
Make the full density plot first

```{r}
base <- ggplot(marathon,
               aes(x = Age, y = ..count..)) + #<<
    geom_density(fill = 'grey', alpha = 0.7) + #<<
    scale_y_continuous(
        expand = expand_scale(mult = c(0, 0.05))) +
    theme_minimal_hgrid()
```
]]
.rightcol[
```{r density_facet_base, echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
base
```
]

---
## How to make density facets

.leftcol[.code70[
Separately create each sub-plot

```{r}
male <- base +
  geom_density(data = marathon %>% #<<
                   filter(`M/F` == 'M'), #<<
               fill = 'steelblue', alpha = 0.7) +
  theme(legend.position = 'none')
```
```{r}
female <- base +
  geom_density(data = marathon %>% #<<
                   filter(`M/F` == 'F'), #<<
               fill = 'sienna', alpha = 0.7) +
  theme(legend.position = 'none')
```
]]
.rightcol[
```{r density_facet_male, echo=FALSE, fig.height=3, fig.width=4, fig.align='center'}
male
```

```{r density_facet_female, echo=FALSE, fig.height=3, fig.width=4, fig.align='center'}
female
```
]

---
## How to make density facets

.leftcol[.code70[
Combine into single plot

```{r, eval=FALSE}
plot_grid(male, female,
          labels = c('Male', 'Female'))
```
]]
.rightcol[
```{r ref.label='marathon_density_facet', echo=FALSE, fig.height=3, fig.width=7, fig.align='center'}
```
]

---
## How to make diverging histograms

.leftcol[.code70[
Make the histograms by filtering the data

```{r marathon_diverging_histograms1, fig.show='hide'}
ggplot(marathon, aes(x = Age)) +
    # Add histogram for Female runners:
    geom_histogram(data = marathon %>% #<<
                       filter(`M/F` == 'F'), #<<
                   aes(fill = `M/F`, y=..count..), #<<
                   alpha = 0.7, color = 'white') +
    # Add negative histogram for Male runners:
    geom_histogram(data = marathon %>%
                       filter(`M/F` == 'M'),
                   aes(fill = `M/F`, y=..count..*(-1)), #<<
                   alpha = 0.7, color = 'white')
```
]]
.rightcol[
```{r ref.label='marathon_diverging_histograms1', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]

---
## How to make diverging histograms

.leftcol[.code70[
Rotate, adjust colors, theme, and annotate

```{r, eval=FALSE}
ggplot(marathon, aes(x = Age)) +
    # Add histogram for Female runners:
    geom_histogram(data = marathon %>%
                       filter(`M/F` == 'F'),
                   aes(fill = `M/F`, y=..count..),
                   alpha = 0.7, color = 'white') +
    # Add negative histogram for Male runners:
    geom_histogram(data = marathon %>%
                       filter(`M/F` == 'M'),
                   aes(fill = `M/F`, y=..count..*(-1)),
                   alpha = 0.7, color = 'white') +
    scale_fill_manual( #<<
        values = c('sienna', 'steelblue')) + #<<
    coord_flip() + #<<
    theme_minimal_hgrid() + #<<
    labs(fill = 'Gender', #<<
         y    = 'Count') #<<
```
]]
.rightcol[
```{r ref.label='marathon_diverging_histograms', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]

---
## How to make ridgeplots

.leftcol[.code70[
Reorder `major_category` variable

```{r, eval=FALSE}
college_summary <- college_all_ages %>%
    mutate(
        major_category = fct_reorder(
            major_category, median))
```

Make the ridgeplot using the **ggridges** library

```{r, eval=FALSE}
library(ggridges) #<<

ggplot(college_summary) +
  geom_density_ridges(aes(x = median, #<<
                          y = major_category), #<<
                      scale = 4, alpha = 0.7) + #<<
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_continuous(expand = c(0, 0)) +
  coord_cartesian(clip = "off") +  #<<
  theme_ridges() +  #<<
  labs(x = 'Median income ($)',
       y = 'Major category')
```
]]
.rightcol[
```{r ref.label='college_ridgeplot', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]

---
class: inverse

## Your turn

Use the `gapminder.csv` data to create the following charts comparing the distribution of life expectancy across countries in continents in 2007.

.leftcol[
```{r, echo=FALSE}
gapminder_2007 <- gapminder %>%
  filter(year == 2007) %>%
  mutate(continent = fct_reorder(continent, lifeExp))
```
```{r gapminder_densities, fig.show='hide', echo=FALSE}
ggplot(gapminder_2007) +
  geom_density(aes(x = lifeExp, y = ..count..,
                   fill = continent), alpha = 0.7) +
  scale_y_continuous(
    expand = expand_scale(mult = c(0, 0.05))) +
  scale_fill_brewer(palette = 'Accent') +
  theme_minimal_hgrid() +
  labs(x = 'Life expectancy (years)',
       y = 'Count',
       fill = 'Continent',
       title = 'Distribution of life expectancy across\ncountries in continent in 2007')
```
```{r ref.label='gapminder_densities', echo=FALSE, fig.height=4.5, fig.width=6.5, fig.align='center'}
```
]
.rightcol[
```{r gapminder_ridges, fig.show='hide', echo=FALSE}
ggplot(gapminder_2007 %>% filter(continent != 'Oceania')) +
    geom_density_ridges(aes(x = lifeExp,
                            y = continent),
                        scale = 1.5, alpha = 0.7) +
    scale_y_discrete(expand = c(0, 0)) +
    scale_x_continuous(expand = c(0, 0)) +
    coord_cartesian(clip = "off") +
    theme_ridges() +
    labs(x = 'Life expectancy (years)',
         y = 'Continent',
         title = 'Distribution of life expectancy across\ncountries in continent in 2007')
```
```{r ref.label='gapminder_ridges', echo=FALSE, fig.height=4.5, fig.width=6.5, fig.align='center'}
```
]
