<!--
Comparing things to a reference line:
- Add a simple line
- diverging bars / lollipops,
- overlapping bars

- In any of these plots, adding a benchmark can be really useful
- examples: dumbbell with benchmark, bullet with benchmark
- Another way is to compare things to a **computed** benchmark, like the mean - diverging bars / lollipops
- Finally, overlapping bars are great when you want to show when something exceeds a threshold. E.g. going over your budget. -->

---
class: center

## Use reference lines to add context to chart

```{r life_expectancy_dots_mean, fig.show='hide', echo=FALSE}
ggplot(gapminder_americas) +
  geom_point(aes(x = lifeExp, y = country),
             color = 'steelblue', size = 2.5) +
  geom_vline(xintercept = mean(gapminder_americas$lifeExp),
             color = 'red', linetype = 'dashed') +
  annotate('text', x = 73, y = 'Puerto Rico',
           color = 'red', hjust = 1,
           label = 'Mean\nLife\nExpectancy') +
  theme_minimal_vgrid() +
  labs(x = 'Life expectancy (years)',
       y = 'Country')
```

.leftcol[
```{r ref.label='life_expectancy_dots', echo=FALSE, fig.height=6, fig.width=6, fig.align='center'}
```
]
--
.rightcol[
```{r ref.label='life_expectancy_dots_mean', echo=FALSE, fig.height=6, fig.width=6, fig.align='center'}
```
]

---
class: center

## Or make zero the reference line

```{r, echo=FALSE}
gapminder_diverging <- gapminder_americas %>%
    mutate(
        lifeExp = lifeExp - mean(lifeExp),
        color = ifelse(lifeExp > 0, 'Above', 'Below'))
```

```{r life_expectancy_dots_diverging, fig.show='hide', echo=FALSE}
ggplot(gapminder_diverging) +
  geom_segment(aes(x = 0, xend = lifeExp,
                   y = country, yend = country,
                   color = color)) +
  geom_point(aes(x = lifeExp, y = country,
                 color = color), size = 2.5) +
  scale_color_manual(values = c('steelblue', 'red')) +
  theme_minimal_vgrid() +
  theme(legend.position = 'none') +
  labs(x = 'Difference from mean life expectancy (years)',
       y = 'Country')
```

```{r life_expectancy_bars_diverging, fig.show='hide', echo=FALSE}
ggplot(gapminder_diverging) +
  geom_col(aes(x = country, y = lifeExp,
               fill = color), width = 0.7, alpha = 0.8) +
  scale_fill_manual(values = c('steelblue', 'red')) +
  coord_flip() +
  theme_minimal_vgrid() +
  theme(legend.position = 'none') +
  labs(x = 'Country',
       y = 'Difference from mean life expectancy (years)')
```

.leftcol[
```{r ref.label='life_expectancy_dots_diverging', echo=FALSE, fig.height=6, fig.width=6, fig.align='center'}
```
]
.rightcol[
```{r ref.label='life_expectancy_bars_diverging', echo=FALSE, fig.height=6, fig.width=6, fig.align='center'}
```
]

---
## Compare multiple references with overlapping bars

```{r overlapping_bars, fig.show='hide', echo=FALSE}
water_usage <- tribble(
    ~'period', ~'current', ~'previous',
    'JAN/FEB',  64, 48,
    'MAR/APR',  52, 46,
    'MAY/JUN',  66, 53,
    'JUL/AUG',  99, 66,
    'SEPT/OCT', 50, 54,
    'NOV/DEC',  52, 49)

ggplot(water_usage) +
    geom_col(aes(x = period, y = previous,
                 fill = '2018'),
             width = 0.7) +
    geom_col(aes(x = period, y = current,
                 fill = '2019'),
             width = 0.3) +
    scale_fill_manual(values = c('grey', 'black')) +
    scale_y_continuous(
        expand = expand_scale(mult = c(0, 0.05))) +
    coord_flip() +
    theme_minimal_vgrid() +
    labs(x = 'Billing period',
         y = 'Cost ($)',
         fill = 'Year',
         title = 'Comparison of water bill in 2018 & 2019')
```
<br>
```{r ref.label='overlapping_bars', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```

---
## How to add a reference line

.leftcol[.code70[
Add horizontal line with `geom_hline()`

Add vertical line with `geom_vline()`

```{r life_expectancy_dots_line, fig.show='hide'}
ggplot(gapminder_americas) +
  geom_point(aes(x = lifeExp, y = country),
             color = 'steelblue', size = 2.5) +
  geom_vline( #<<
      xintercept = mean(gapminder_americas$lifeExp), #<<
      color = 'red', linetype = 'dashed') + #<<
  theme_minimal_vgrid() +
  labs(x = 'Life expectancy (years)',
       y = 'Country')
```
]]
.rightcol[.center[
```{r ref.label='life_expectancy_dots_line', echo=FALSE, fig.height=6, fig.width=6, fig.align='center'}
```
]]

---
## How to add a reference line

.leftcol[.code70[
Add text with `annotate()`
```{r, eval=FALSE}
ggplot(gapminder_americas) +
  geom_point(aes(x = lifeExp, y = country),
             color = 'steelblue', size = 2.5) +
  geom_vline(
      xintercept = mean(gapminder_americas$lifeExp),
      color = 'red', linetype = 'dashed') +
  annotate('text', x = 73, y = 'Puerto Rico', #<<
           color = 'red', hjust = 1, #<<
           label = 'Mean\nLife\nExpectancy') + #<<
  theme_minimal_vgrid() +
  labs(x = 'Life expectancy (years)',
       y = 'Country')
```
]]
.rightcol[.center[
```{r ref.label='life_expectancy_dots_mean', echo=FALSE, fig.height=6, fig.width=6, fig.align='center'}
```
]]

---
## How to make zero the reference point

.leftcol[.code70[
```{r, eval=FALSE}
gapminder_diverging <- gapminder_americas %>%
    mutate(
        lifeExp = lifeExp - mean(lifeExp), #<<
        color = ifelse(lifeExp > 0, 'Above', 'Below')) #<<
```
```{r, eval=FALSE}
ggplot(gapminder_diverging) +
  geom_col(aes(x = country, y = lifeExp,
               fill = color),
           width = 0.7, alpha = 0.8) +
  scale_fill_manual(values = c('steelblue', 'red')) + #<<
  coord_flip() +
  theme_minimal_vgrid() +
  theme(legend.position = 'none') +
  labs(
    x = 'Country',
    y = 'Difference from mean life expectancy (years)')
```
]]
.rightcol[
```{r ref.label='life_expectancy_bars_diverging', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]

---
## How to make overlapping bars

.leftcol[.code60[
```{r, echo=FALSE}
water_usage
```
```{r, eval=FALSE}
ggplot(water_usage) +
    geom_col(aes(x = period, y = previous,
                 fill = '2018'), #<<
             width = 0.7) + #<<
    geom_col(aes(x = period, y = current,
                 fill = '2019'), #<<
             width = 0.3) + #<<
    scale_fill_manual(values = c('grey', 'black')) + #<<
    scale_y_continuous(
        expand = expand_scale(mult = c(0, 0.05))) +
    coord_flip() +
    theme_minimal_vgrid() +
    labs(x = 'Billing period',
         y = 'Cost ($)',
         fill = 'Year',
         title = 'Comparison of water bill in 2018 & 2019')
```
]]
.rightcol[.center[
```{r ref.label='overlapping_bars', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]]

---
class: inverse

### Your turn

Use the `milk_production.csv` data to create the following charts<br>showing differences from the mean state milk production in 2017.

```{r milk_lollipop_mean, fig.show='hide', echo=FALSE}
milk_summary <- milk_production %>%
  filter(year == 2017) %>%
  mutate(
    milk_produced = milk_produced / 10^9,
    state = fct_reorder(state, milk_produced))

ggplot(milk_summary) +
  geom_point(aes(x = milk_produced, y = state),
             size = 2.5, color = 'steelblue') +
  geom_vline(xintercept = mean(milk_summary$milk_produced),
             color = 'red', linetype = 'dashed') +
  annotate('text', x = 5, y = 'Georgia',
           color = 'red', hjust = 0,
           label = 'Mean\nProduction') +
  theme_minimal_vgrid() +
  labs(x = 'Milk produced (billions lbs)',
       y = 'State')
```
```{r milk_bars_diverging, fig.show='hide', echo=FALSE}
milk_summary_diverging <- milk_summary %>%
  mutate(
    milk_produced = milk_produced - mean(milk_produced),
    barColor = ifelse(milk_produced > 0, 'above', 'below'))

ggplot(milk_summary_diverging) +
  geom_col(aes(x = state, y = milk_produced,
               fill = barColor), width = 0.7) +
  scale_fill_manual(values = c('steelblue', 'sienna')) +
  coord_flip() +
  theme_minimal_vgrid() +
  theme(legend.position = 'none') +
  labs(x = 'State',
       y = 'Difference from mean milk produced (billions lbs)')
```

.leftcol[
```{r ref.label='milk_lollipop_mean', echo=FALSE, fig.height=6.3, fig.width=5, fig.align='center'}
```
]
.rightcol[
```{r ref.label='milk_bars_diverging', echo=FALSE, fig.height=6.3, fig.width=5, fig.align='center'}
```
]
