---
title: "Week 7: Data cleaning & joins"
author: "John Paul Helveston"
date: February 26, 2020
output:
  xaringan::moon_reader:
    css: ['default', 'https://emse-eda-gwu.github.io/2020-Spring/classNotes/classNotes.css']
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      beforeInit: "https://platform.twitter.com/widgets.js"
    seal: false
---

```{r setup, include=FALSE}
library(here)
source(here::here('setup.R'))
```

name: xaringan-title
class: title-slide, center, middle, inverse

# Week 7: Data cleaning & joins

.large[EMSE 4197 | John Paul Helveston | February 26, 2020]

```{r child = here::here('parts', 'intro.Rmd')}
```

---
class: inverse, middle

# Data cleaning & joins

## 1. Joins
## 2. Re-typing variables
## 3. Re-naming variables
## 4. Re-coding variables
## 5. Data cleaning strategies

---
class: inverse, middle

# Data cleaning & joins

## 1. .orange[Joins]
## 2. Re-typing variables
## 3. Re-naming variables
## 4. Re-coding variables
## 5. Data cleaning strategies

```{r child = here::here('parts', 'joins.Rmd')}
```

---
class: inverse, middle

# Data cleaning & joins

## 1. Joins
## 2. .orange[Re-typing variables]
## 3. Re-naming variables
## 4. Re-coding variables
## 5. Data cleaning strategies

```{r child = here::here('parts', 'retyping.Rmd')}
```

---
class: inverse, middle

# Data cleaning & joins

## 1. Joins
## 2. Re-typing variables
## 3. .orange[Re-naming variables]
## 4. Re-coding variables
## 5. Data cleaning strategies

```{r child = here::here('parts', 'renaming.Rmd')}
```

---
class: inverse

# 5 minute break!

```{r, echo=FALSE}
countdown(minutes = 5,
          warn_when = 30,
          left = 0,
          font_size = '5em')
```

## Stand up

## Move around

## Stretch!

---
class: inverse, middle

# Data cleaning & joins

## 1. Joins
## 2. Re-typing variables
## 3. Re-naming variables
## 4. .orange[Re-coding variables]
## 5. Data cleaning strategies

```{r child = here::here('parts', 'recoding.Rmd')}
```

---
class: inverse, middle

# Data cleaning & joins

## 1. Joins
## 2. Re-typing variables
## 3. Re-naming variables
## 4. Re-coding variables
## 5. .orange[Data cleaning strategies]

```{r child = here::here('parts', 'strategies.Rmd')}
```

---
class: inverse, middle

## If you haven't already, now would be a good time to start working on your projects

<br>

## **You have 2 weeks until proposals are due**

---
# Writing a research question

Following [these guidelines](https://writingcenter.gmu.edu/guides/how-to-write-a-research-question), your question should be:

- **Clear**: your audience can easily understand its purpose without additional explanation.
- **Focused**: it is narrow enough that it can be addressed thoroughly with the data available and within the limits of the final project report.
- **Concise**: it is expressed in the fewest possible words.
- **Complex**: it is not answerable with a simple "yes" or "no," but rather requires synthesis and analysis of data.
- **Arguable**: its potential answers are open to debate rather than accepted facts (do others care about it?)
