<!--
Most of this content came from this presentation:
https://designing-ggplots.netlify.com/#1
-->

```{r milk_region_line, fig.show='hide', echo=FALSE}
ggplot(milk_region,
    aes(x = year, y = milk_produced,
        color = region)) +
    geom_line(size = 1) +
    scale_color_manual(values = c(
        'sienna', 'forestgreen', 'dodgerblue', 'orange')) +
    theme_half_open(font_size = 18) +
    labs(x = 'Year',
         y = 'Milk produced (billion lbs)',
         color = 'Region',
         title = 'Milk production in four US regions')
```
```{r milk_region_line_label, fig.show='hide', echo=FALSE}
ggplot(milk_region,
    aes(x = year, y = milk_produced,
        color = region)) +
    geom_line(size = 1) +
    geom_text(aes(label = label),
              hjust = 0, nudge_x = 1,
              size = 6) +
    scale_color_manual(values = c(
        'sienna', 'forestgreen', 'dodgerblue', 'orange')) +
    coord_cartesian(clip = 'off') +
    theme_half_open(font_size = 18) +
    theme(legend.position = 'none',
          plot.margin = margin(0.1, 2.7, 0.1, 0.1, "cm")) +
    labs(x = 'Year',
         y = 'Milk produced (billion lbs)',
         title = 'Milk production in four US regions')
```
```{r fed_spending_legend, fig.show='hide', echo=FALSE}
ggplot(federal_spending_summary) +
    geom_area(aes(x = year, y = rd_budget,
                  fill = department)) +
    scale_y_continuous(
        expand = expand_scale(mult = c(0, 0.05))) +
    scale_fill_manual(values = c('grey', 'sienna')) +
    theme_minimal_hgrid() +
    labs(x = NULL,
         y = 'R&D Budget ($ Billions)',
         fill = 'Department',
         title = 'Federal R&D spending, 1976 - 2017',
         subtitle = 'Data Source: AAAS Historical Trends')
```
```{r, fed_spending_annotate, fig.show='hide', echo=FALSE}
ggplot(federal_spending_summary) +
    geom_area(aes(x = year, y = rd_budget,
                  fill = department)) +
    annotate(geom = 'text', x = 1995, y = 85,  #<<
             label = 'Other', size = 6, color = 'black') + #<<
    annotate(geom = 'text', x = 1995, y = 25, #<<
             label = 'DOD', size = 6, color = 'white') + #<<
    scale_y_continuous(
        expand = expand_scale(mult = c(0, 0.05))) +
    scale_fill_manual(values = c('grey', 'sienna')) +
    theme_minimal_hgrid() +
    theme(legend.position = 'none') +
    labs(x = NULL,
         y = 'R&D Budget ($ Billions)',
         title = 'Federal R&D spending, 1976 - 2017',
         subtitle = 'Data Source: AAAS Historical Trends')
```
```{r, fed_spending_geom_text, fig.show='hide', echo=FALSE}
ggplot(federal_spending_summary) +
    geom_area(aes(x = year, y = rd_budget,
                  fill = department)) +
    geom_text(aes(x = 1995, y = 85, label = 'Other'), #<<
              size = 6, color = 'black') + #<<
    geom_text(aes(x = 1995, y = 25, label = 'DOD'), #<<
              size = 6, color = 'white') + #<<
    scale_y_continuous(
        expand = expand_scale(mult = c(0, 0.05))) +
    scale_fill_manual(values = c('grey', 'sienna')) +
    theme_minimal_hgrid() +
    theme(legend.position = 'none') +
    labs(x = NULL,
         y = 'R&D Budget ($ Billions)',
         title = 'Federal R&D spending, 1976 - 2017',
         subtitle = 'Data Source: AAAS Historical Trends')
```
```{r, fed_spending_geom_label, fig.show='hide', echo=FALSE}
ggplot(federal_spending_summary) +
    geom_area(aes(x = year, y = rd_budget,
                  fill = department)) +
    geom_label(aes(x = 1995, y = 85, label = 'Other'), #<<
               size = 6) + #<<
    geom_label(aes(x = 1995, y = 25, label = 'DOD'), #<<
               size = 6) + #<<
    scale_y_continuous(
        expand = expand_scale(mult = c(0, 0.05))) +
    scale_fill_manual(values = c('grey', 'sienna')) +
    theme_minimal_hgrid() +
    theme(legend.position = 'none') +
    labs(x = NULL,
         y = 'R&D Budget ($ Billions)',
         title = 'Federal R&D spending, 1976 - 2017',
         subtitle = 'Data Source: AAAS Historical Trends')
```
---
class: center, middle

# Legends suck

--
.leftcol[
### Legends require look-up task

```{r ref.label='milk_region_line', echo=FALSE, fig.height=5, fig.width=7.5, fig.align='center'}
```
]
--
.rightcol[
### Direct labeling is much better

```{r ref.label='milk_region_line_label', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]

---
class: center, middle

# Legends suck

.leftcol[
### Legends require look-up task

```{r ref.label='fed_spending_legend', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]
--
.rightcol[
### Direct labeling is much better

```{r ref.label='fed_spending_annotate', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]

---
## Use `annotate()` to add text to chart

.leftcol60[.code70[
```{r}
dod_spending <- ggplot(federal_spending_summary) +
    geom_area(aes(x = year, y = rd_budget,
                  fill = department)) +
    annotate(geom = 'text', x = 1995, y = 85,  #<<
             label = 'Other', size = 6, color = 'black') + #<<
    annotate(geom = 'text', x = 1995, y = 25, #<<
             label = 'DOD', size = 6, color = 'white') + #<<
    scale_y_continuous(
        expand = expand_scale(mult = c(0, 0.05))) +
    scale_fill_manual(values = c('grey', 'sienna')) +
    theme_minimal_hgrid() +
    theme(legend.position = 'none') +
    labs(x = NULL,
         y = 'R&D Budget ($ Billions)',
         title = 'Federal R&D spending, 1976 - 2017',
         subtitle = 'Data Source: AAAS Historical Trends')
```
]]
.rightcol40[
<br>
```{r ref.label='fed_spending_annotate', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]

---
## Use `geom_text()` to add text to chart

.leftcol60[.code70[
```{r, eval=FALSE}
dod_spending <- ggplot(federal_spending_summary) +
    geom_area(aes(x = year, y = rd_budget,
                  fill = department)) +
    geom_text(aes(x = 1995, y = 85, label = 'Other'), #<<
              size = 6, color = 'black') + #<<
    geom_text(aes(x = 1995, y = 25, label = 'DOD'), #<<
              size = 6, color = 'white') + #<<
    scale_y_continuous(
        expand = expand_scale(mult = c(0, 0.05))) +
    scale_fill_manual(values = c('grey', 'sienna')) +
    theme_minimal_hgrid() +
    theme(legend.position = 'none') +
    labs(x = NULL,
         y = 'R&D Budget ($ Billions)',
         title = 'Federal R&D spending, 1976 - 2017',
         subtitle = 'Data Source: AAAS Historical Trends')
```
]]
.rightcol40[
<br>
```{r ref.label='fed_spending_geom_text', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]

---
## Use `geom_label()` to add text to chart<br>**with a background**

.leftcol60[.code70[
```{r, eval=FALSE}
dod_spending <- ggplot(federal_spending_summary) +
    geom_area(aes(x = year, y = rd_budget,
                  fill = department)) +
    geom_label(aes(x = 1995, y = 85, label = 'Other'), #<<
               size = 6) + #<<
    geom_label(aes(x = 1995, y = 25, label = 'DOD'), #<<
               size = 6) + #<<
    scale_y_continuous(
        expand = expand_scale(mult = c(0, 0.05))) +
    scale_fill_manual(values = c('grey', 'sienna')) +
    theme_minimal_hgrid() +
    theme(legend.position = 'none') +
    labs(x = NULL,
         y = 'R&D Budget ($ Billions)',
         title = 'Federal R&D spending, 1976 - 2017',
         subtitle = 'Data Source: AAAS Historical Trends')
```
]]
.rightcol40[
<br>
```{r ref.label='fed_spending_geom_label', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]

---
### Use `geom_curve()` + `geom_label()` to direct attention

.leftcol60[.code70[
Make the label
```{r}
label <- "The Dept. of Defense R&D Budget
has made up nearly half of all
federal R&D spending"
```
Add label with curved arrow
```{r fed_spending_curve, fig.show='hide'}
dod_spending +
    geom_curve( #<<
        aes(x = 1981, xend = 1987, #<<
            y = 160, yend = 25),#<<
        size = 0.5,
        curvature = 0.1,
        arrow = arrow(length = unit(0.01, "npc"), #<<
                      type = "closed") #<<
    ) +
    geom_label(
        aes(x = 1977, y = 160, label = label),
        hjust = 0, lineheight = 0.8
    )
```
]]
.rightcol40[
<br>

```{r ref.label='fed_spending_curve', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]

---
## Use `annotate()` to direct attention

.leftcol60[.code70[
Use `geom = "rect"` for box, `geom = "text"` for label
```{r mpg_box, fig.show='hide'}
ggplot(mpg, aes(x = displ, y = hwy)) +
    geom_point(aes(fill = as.factor(cyl)),
               color = 'white', alpha = 0.8,
               size = 3.5, shape = 21) +
    annotate(geom = "rect", #<<
             xmin = 5, xmax = 7.5, #<<
             ymin = 21, ymax = 28, #<<
             fill = "grey55", alpha = 0.2) + #<<
    annotate(geom = "text",
             x = 5, y = 29,
             label = "Hybrid vehicles",
             hjust = 0, size = 5) +
    theme_half_open(font_size = 15) +
    labs(x = "Engine displacement",
         y = "Fuel efficiency (mpg)",
         fill = '# cylinders',
         title = "Vehicle fuel efficiency vs. engine displacement",
         caption = "Data source: U.S. EPA.")
```
]]
.rightcol40[
<br>

```{r ref.label='mpg_box', echo=FALSE, fig.height=6, fig.width=7, fig.align='center'}
```
]

---
class: inverse

## Your turn

```{r wildlife_costs_annotated, fig.show='hide', echo=FALSE}
label <- "US Airways Flight 1549
was crash landed into the
Hudson river after striking a 
flock of Canada geese on 
Jan. 15, 2009."

ggplot(wildlife_costs) + 
    geom_point(aes(x = incident_date, y = cost)) + 
    geom_curve(
        mapping = aes(x = ymd('2000-01-01'),
                      xend = ymd('2008-10-01'), 
                      y = 13, yend = 16.4),
        color = 'grey75', size = 0.5, curvature = -0.2,
        arrow = arrow(length = unit(0.01, 'npc'), type = 'closed')) +
    geom_label(
        mapping = aes(x = ymd('1995-01-01'), y = 13,
                      label = label),
        hjust = 0, lineheight = .8) +
    scale_x_date(
        date_breaks = '3 years',
        date_labels = "'%y") + 
    scale_y_continuous(
        labels = scales::dollar,
        expand = expand_scale(mult = c(0, 0.05))) +
    theme_minimal_grid(font_size = 16) + 
    labs(x = 'Year', 
         y = 'Cost of incident repairs ($ millions)', 
         title = 'Repair costs of aircraft impacts with wildlife', 
         subtitle = 'Top 4 airlines', 
         caption = 'Data source: https://wildlife.faa.gov/home')
```

.leftcol[
Use the `wildlife_costs` data frame to create the following chart. 
.font90[
Hints:

- Use the **lubridate** package to create dates.
- For the `geom_label()`, use these points:
    - `x = ymd('1995-01-01')`
    - `y = 13`
- For the `geom_curve()`, use these points:
    - `x = ymd('2000-01-01')`
    - `xend = ymd('2008-10-01')`
    - `y = 13`
    - `yend = 16.4`
]]
.rightcol[
```{r ref.label='wildlife_costs_annotated', echo=FALSE, fig.height=5, fig.width=7, fig.align='center'}
```
]
