---
title: "Week 8: Polishing your charts"
author: "John Paul Helveston"
date: March 04, 2020
output:
  xaringan::moon_reader:
    css: ['default', 'https://emse-eda-gwu.github.io/2020-Spring/classNotes/classNotes.css']
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      beforeInit: "https://platform.twitter.com/widgets.js"
    seal: false
---

```{r setup, include=FALSE}
library(here)
source(here('setup.R'))
```

---
class: inverse, center, middle 

# How to customize fonts in **ggplot**

---
## 1. Change the whole theme

.leftcol[.code70[
For "Base R" themes, use `base_family`:

```{r, eval=FALSE}
theme_minimal(base_family = "Roboto Condensed")
```
```{r, eval=FALSE}
theme_bw(base_family = "Roboto Condensed")
```
]]
.rightcol[.code70[
For "cowplot" themes, use `font_family`:

```{r, eval=FALSE}
theme_half_open(font_family = "Roboto Condensed")
```
```{r, eval=FALSE}
theme_minimal_grid(font_family = "Roboto Condensed")
```
]]

---
## 1. Change the whole theme font

.leftcol60[.code70[
Summarise the data
```{r, eval=FALSE}
lotr_summary <- lotr_words %>% 
    gather(key = 'gender', value = 'wordCount', 
           Female:Male)
```
Make the base plot
```{r lotr, fig.show='hide'}
lotr_plot <- ggplot(lotr_summary) + 
    geom_col(aes(x = gender, y = wordCount, 
                 fill = gender), 
             width = 0.7) + 
    facet_wrap(~Race) +
    scale_y_continuous(
        labels = scales::comma,
        expand = expand_scale(mult = c(0, 0.05))) +
    theme_minimal(base_size = 15) + #<<
    theme(legend.position = 'none') +
    labs(x = 'Gender of character',
         y = 'Number of words spoken', 
         title = 'Number of words spoken in LOTR trilogy')
```
]]

<br>

.rightcol40[
```{r, echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
lotr_plot
```
]

---
## 1. Change the whole theme font

.leftcol60[.code70[
Use `base_family` with base themes
```{r lotr_base, fig.show='hide'}
lotr_plot <- ggplot(lotr_summary) + 
    geom_col(aes(x = gender, y = wordCount, 
                 fill = gender), 
             width = 0.7) + 
    facet_wrap(~Race) +
    scale_y_continuous(
        labels = scales::comma,
        expand = expand_scale(mult = c(0, 0.05))) +
    theme_minimal(base_family = 'Source Sans Pro', #<<
                  base_size = 15) + 
    theme(legend.position = 'none') +
    labs(x = 'Gender of character',
         y = 'Number of words spoken', 
         title = 'Number of words spoken in LOTR trilogy')
```
]]

<br>

.rightcol40[
```{r, echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
lotr_plot
```
]

---
## 1. Change the whole theme font

.leftcol60[.code70[
Use `font_family` with cowplot themes
```{r lotr_cowplot, fig.show='hide'}
lotr_plot <- ggplot(lotr_summary) + 
    geom_col(aes(x = gender, y = wordCount, 
                 fill = gender), 
             width = 0.7) + 
    facet_wrap(~Race) +
    scale_y_continuous(
        labels = scales::comma,
        expand = expand_scale(mult = c(0, 0.05))) +
    theme_minimal_hgrid(font_family = 'Source Sans Pro', #<<
                  font_size = 15) +
    theme(legend.position = 'none') +
    panel_border() +
    labs(x = 'Gender of character',
         y = 'Number of words spoken', 
         title = 'Number of words spoken in LOTR trilogy')
```
]]

<br>

.rightcol40[
```{r, echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
lotr_plot
```
]

---
## 2. Adjust theme elements with `element_text()`

.leftcol60[.code70[
Use `font_family` with cowplot themes
```{r lotr_cowplot_title, fig.show='hide'}
lotr_plot <- ggplot(lotr_summary) + 
    geom_col(aes(x = gender, y = wordCount, 
                 fill = gender), 
             width = 0.7) + 
    facet_wrap(~Race) +
    scale_y_continuous(
        labels = scales::comma,
        expand = expand_scale(mult = c(0, 0.05))) +
    theme_minimal_hgrid(font_family = 'Source Sans Pro',
                  font_size = 15) +
    theme(legend.position = 'none',
          plot.title = element_text(family = "Roboto Condensed", #<<
                                    size = 20)) + 
    panel_border() +
    labs(x = 'Gender of character',
         y = 'Number of words spoken', 
         title = 'Number of words spoken in LOTR trilogy')
```
]]

<br>

.rightcol40[
```{r, echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
lotr_plot
```
]

---
### 3. Adjust annotations (`geom_text()` and `annotate()`)

.leftcol60[.code70[
```{r lotr_cowplot_annotate, fig.show='hide'}
lotr_plot +
    # Draw curved arrow
    geom_curve(
        data = data.frame(x = 0.8, y = 1200,
                          xend = 1, yend = 200,
                          Race = 'Hobbit'),
        mapping = aes(x = x, y = y, xend = xend, yend = yend),
        color = "grey75",
        size = 0.5,
        curvature = 0.1,
        arrow = arrow(length = unit(0.01, "npc"), type = "closed")
    ) +
    # Add annotation
    geom_label(
        data = data.frame(x = 0.47, y = 2000,
                          label = label, Race = 'Hobbit'),
        mapping = aes(x = x, y = y, label = label),
        hjust = 0, 
        lineheight = .8, 
        family = 'Roboto Condensed' #<<
    )
```
]]

<br>

.rightcol40[
```{r ref.label='lotr_cowplot_annotate', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]

---
## The [hrbrthemes](https://github.com/hrbrmstr/hrbrthemes) package: 

### Great themes + great fonts

.leftcol[
```{r mpg_ipsum, fig.show='hide'}
library(hrbrthemes) #<<

ggplot(mtcars, aes(mpg, wt)) +
  geom_point() +
  labs(x="Fuel efficiency (mpg)", y="Weight (tons)",
       title="Seminal ggplot2 scatterplot example",
       subtitle="A plot that is only useful for demonstration purposes",
       caption="Brought to you by the letter 'g'") + 
  theme_ipsum() #<<
```

]
.rightcol[
```{r ref.label='mpg_ipsum', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]

---
## Other great themes that also change the font

### (and a bunch of other stuff)

.leftcol[
```{r mpg_ipsum_rc, fig.show='hide'}
library(hrbrthemes) #<<

ggplot(mtcars, aes(mpg, wt)) +
  geom_point() +
  labs(x="Fuel efficiency (mpg)", y="Weight (tons)",
       title="Seminal ggplot2 scatterplot example",
       subtitle="A plot that is only useful for demonstration purposes",
       caption="Brought to you by the letter 'g'") + 
  theme_ipsum_rc() #<<
```

]
.rightcol[
```{r ref.label='mpg_ipsum_rc', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]

---
## Other great themese that also change the font

### (and a bunch of other stuff)

.leftcol[
```{r mpg_ft_rc, fig.show='hide'}
library(hrbrthemes) #<<

ggplot(mtcars, aes(mpg, wt)) +
  geom_point() +
  labs(x="Fuel efficiency (mpg)", y="Weight (tons)",
       title="Seminal ggplot2 scatterplot example",
       subtitle="A plot that is only useful for demonstration purposes",
       caption="Brought to you by the letter 'g'") + 
  theme_ft_rc() #<<
```

]
.rightcol[
```{r ref.label='mpg_ft_rc', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]