---
title: "Week 1 In Class Notes"
output: html_document
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
options(
    htmltools.dir.version = FALSE,
    knitr.table.format = "html",
    knitr.kable.NA = '')
knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.retina = 3)
```

# Importing data

Read in .csv files with read_csv():
```{r}
csvPath <- here('data', 'milk_production.csv')
milk_production <- read_csv(csvPath)
```

Read in .txt files with read.table():
```{r}
txtPath <- here('data', 'nasa_global_temps.txt')
global_temps <- read.table(txtPath, skip = 5, header = FALSE)
# Rename the variables
names(global_temps) <- c('year', 'meanTemp', 'smoothTemp')
```

Read in .xlsx files with read_excel():
```{r}
library(readxl)
xlsxPath <- here('data', 'pv_cell_production.xlsx')
pv_cells <- read_excel(xlsxPath, sheet = 'Cell Prod by Country', skip = 2)
# Drop rows that don't contain data
pv_cells <- pv_cells %>%
    filter(is.na(Year) == FALSE, Year <= 2013)
```




# Importing data practice:

Write code to import the following files inside the "data" folder:

- wildlife_impacts.csv
- north_america_bear_killings.txt
- pc_sales_2018.xlsx

```{r}
# Insert code here
```


# Data provenance practice:

URLs to the original data sources:

- wildlife_impacts.csv: https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-07-23
- north_america_bear_killings.txt: https://data.world/makeovermonday/2019w21
- pc_sales_2018.xlsx: http://www.oica.net/category/sales-statistics/

Go to each of the above sites, then add the following information about the data to the "data_sources.txt" file:

- The name of the downloaded file in the "`data`" folder.
- The date you downloaded the file (i.e. today's date).
- The url to the site you downloaded the data from.
- The source of the _original_ data (if different from where you downloaded the data).
- A short description of the data and how they were collected.
- A dictionary for the data (if available).




# Tidy data

Read in data:
```{r}
library(readxl)
xlsxPath <- here('data', 'pv_cell_production.xlsx')
pv_cells <- read_excel(xlsxPath, sheet = 'Cell Prod by Country', skip = 2) %>%
    filter(is.na(Year) == FALSE, Year <= 2013)
```

Convert to "long" format (tidy):
```{r}
pv_cells_long <- pv_cells %>%
    gather(key = 'Country', value = 'nPVCells', China:World)
```

Convert to "wide" format (un-tidy):
```{r}
pv_cells_wide <- pv_cells_long %>%
    spread(key = Country, value = nPVCells)
```




# Tidy data practice 1: wide to long

1. Read in the `lotr_words.csv` data file.
2. Use `gather()` to "tidy" the data into four columns: Film, Race, Gender, Words.
3. Use `write_csv()` and `here()` to save your file at `lotr_words_tidy.csv` in the `data` folder.

```{r}
# Insert code here
```

# Tidy data practice 2: long to wide

1. Read in the `lotr_words_tidy.csv` data file.
2. Use `spread()` to convert the "tidy" data back into it's untidy format with the columns: Film, Race, Female, Male.

```{r}
# Insert code here
```