---
title: "Week 8: Polishing your charts"
author: "John Paul Helveston"
date: March 04, 2020
output:
  xaringan::moon_reader:
    css: ['default', 'https://emse-eda-gwu.github.io/2020-Spring/classNotes/classNotes.css']
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      beforeInit: "https://platform.twitter.com/widgets.js"
    seal: false
---

```{r setup, include=FALSE}
library(here)
source(here::here('setup.R'))
```

name: xaringan-title
class: title-slide, center, middle, inverse

# Week 8: Polishing your charts

.large[EMSE 4197 | John Paul Helveston | March 04, 2020]

```{r child = here::here('parts', 'intro.Rmd')}
```

---
class: inverse, middle

# Polishing your charts

## 1. Scales
## 2. Annotations
## 3. Colors
## 4. Fonts
## 5. Rmd tricks

---
class: inverse, middle

# Polishing your charts

## 1. .orange[Scales]
## 2. Annotations
## 3. Colors
## 4. Fonts
## 5. Rmd tricks

```{r child = here::here('parts', 'scales.Rmd')}
```

---
class: inverse, middle

# Polishing your charts

## 1. Scales
## 2. .orange[Annotations]
## 3. Colors
## 4. Fonts
## 5. Rmd tricks

```{r child = here::here('parts', 'annotations.Rmd')}
```

---
class: inverse

# 5 minute break!

```{r, echo=FALSE}
countdown(minutes = 5,
          warn_when = 30,
          left = 0,
          font_size = '5em')
```

## Stand up

## Move around

## Stretch!

---
class: inverse, middle

# Polishing your charts

## 1. Scales
## 2. Annotations
## 3. .orange[Colors]
## 4. Fonts
## 5. Rmd tricks

```{r child = here::here('parts', 'colors.Rmd')}
```

---
class: inverse, middle

# Polishing your charts

## 1. Scales
## 2. Annotations
## 3. Colors
## 4. .orange[Fonts]
## 5. Rmd tricks

```{r child = here::here('parts', 'fonts.Rmd')}
```

---
class: inverse, middle

# Polishing your charts

## 1. Scales
## 2. Annotations
## 3. Colors
## 4. Fonts
## 5. .orange[Rmd tricks]

```{r child = here::here('parts', 'rmd.Rmd')}
```

```{r child = here::here('parts', 'extra.Rmd')}
```
