---
title: "Week 6: Graphing trends"
author: "John Paul Helveston"
date: February 19, 2020
output:
  xaringan::moon_reader:
    css: ['default', 'https://emse-eda-gwu.github.io/2020-Spring/classNotes/classNotes.css']
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      beforeInit: "https://platform.twitter.com/widgets.js"
    seal: false
---

```{r setup, include=FALSE}
library(here)
source(here('setup.R'))
```

name: xaringan-title
class: title-slide, center, middle, inverse

# Week 6: Graphing trends

.large[EMSE 4197 | John Paul Helveston | February 19, 2020]

---
class: inverse, middle, center

# Quiz 2

# [25 minutes](https://www.youtube.com/watch?v=ddL3y1saEJs)

```{r child = here('parts', 'intro.Rmd')}
```

---
class: inverse, middle

# Graphing trends

## 1. Single variables
## 2. Multiple variables
## 3. Animations

---
class: inverse, middle

# Graphing trends

## 1. .orange[Single variables]
## 2. Multiple variables
## 3. Animations

```{r child = here('parts', 'single.Rmd')}
```

---
class: inverse, middle

# Graphing trends

## 1. Single variables
## 2. .orange[Multiple variables]
## 3. Animations

```{r child = here('parts', 'multi.Rmd')}
```

---
class: inverse

# [5 minute](https://www.youtube.com/watch?v=_W0bSen8Qjg) break!

## Stand up

## Move around

## Stretch!

---
class: inverse, middle

# Graphing trends

## 1. Single variables
## 2. Multiple variables
## 3. .orange[Animations]

```{r child = here('parts', 'animations.Rmd')}
```
