
```{r milk_ca_point, fig.show='hide', echo=FALSE}
ggplot(milk_ca,
    aes(x = year, y = milk_produced)) +
    geom_point(color = 'steelblue', size = 2) +
    theme_half_open(font_size = 18) +
    labs(x = 'Year',
         y = 'Milk produced (billion lbs)',
         title = 'Milk production in California')
```
```{r milk_ca_point_line, fig.show='hide', echo=FALSE}
ggplot(milk_ca,
    aes(x = year, y = milk_produced)) +
    geom_point(color = 'steelblue', size = 2) +
    geom_line(color = 'steelblue', size = 0.5) +
    theme_half_open(font_size = 18) +
    labs(x = 'Year',
         y = 'Milk produced (billion lbs)',
         title = 'Milk production in California')
```
```{r milk_ca_line, fig.show='hide', echo=FALSE}
ggplot(milk_ca,
    aes(x = year, y = milk_produced)) +
    geom_line(color = 'steelblue', size = 1) +
    theme_half_open(font_size = 18) +
    labs(x = 'Year',
         y = 'Milk produced (billion lbs)',
         title = 'Milk production in California')
```
```{r milk_ca_line_area, fig.show='hide', echo=FALSE}
ggplot(milk_ca,
    aes(x = year, y = milk_produced)) +
    geom_line(color = 'steelblue', size = 1) +
    geom_area(fill = 'steelblue', alpha = 0.5) +
    scale_y_continuous(expand = expand_scale(mult = c(0, 0.05))) +
    theme_half_open(font_size = 18) +
    labs(x = 'Year',
         y = 'Milk produced (billion lbs)',
         title = 'Milk production in California')
```
```{r milk_ca_point_line_sparse1, fig.show='hide', echo=FALSE}
ggplot(milk_ca_sparse,
       aes(x = year, y = milk_produced)) +
    geom_line(color = 'steelblue', size = 0.5) +
    geom_point(aes(color = yearColor), size = 2) +
    scale_color_manual(values = c('red', 'steelblue')) +
    theme_half_open(font_size = 18) +
    theme(legend.position = 'none') +
    labs(x = 'Year',
         y = 'Milk produced (billion lbs)',
         title = 'Milk production in California')
```
```{r milk_ca_point_line_sparse2, fig.show='hide', echo=FALSE}
ggplot(milk_ca_sparse %>%
           filter(yearColor == 'one'),
       aes(x = year, y = milk_produced)) +
    geom_line(color = 'steelblue', size = 0.5) +
    geom_point(color = 'red', size = 2) +
    theme_half_open(font_size = 18) +
    labs(x = 'Year',
         y = 'Milk produced (billion lbs)',
         title = 'Milk production in California')
```
```{r milk_ca_smooth, fig.show='hide', echo=FALSE}
ggplot(milk_ca,
    aes(x = year, y = milk_produced)) +
    geom_smooth(color = 'steelblue', size = 1, se = FALSE) +
    theme_half_open(font_size = 18) +
    labs(x = 'Year',
         y = 'Milk produced (billion lbs)',
         title = 'Milk production in California')
```
```{r milk_ca_smooth_points, fig.show='hide', echo=FALSE}
ggplot(milk_ca,
    aes(x = year, y = milk_produced)) +
    geom_point(color = 'grey', size = 2, alpha = 0.9) +
    geom_smooth(color = 'steelblue', size = 1, se = FALSE) +
    theme_half_open(font_size = 18) +
    labs(x = 'Year',
         y = 'Milk produced (billion lbs)',
         title = 'Milk production in California')
```
```{r hotdog_bar_record, fig.show='hide', echo=FALSE}
ggplot(hotdogs_mens) +
    geom_col(aes(x = Year, y = dogs, fill = record),
             width = 0.8, alpha = 0.9) +
    scale_fill_manual(values = c("grey", "sienna")) +
    scale_y_continuous(expand = expand_scale(mult = c(0, 0.05))) +
    theme_minimal_hgrid() +
    theme(legend.position = c(0.1, 0.65)) +
    labs(x = 'Year',
         y = 'Number of hot dogs & buns\nin 10 minutes',
         fill = 'Record\nbroken?',
         title = "Record-breaking wins in Nathan's hot dog\neating competition, men's division")
```
```{r hotdog_bar_winner, fig.show='hide', echo=FALSE}
ggplot(hotdogs_mens) +
    geom_col(aes(x = Year, y = dogs, fill = Winner),
             width = 0.8, alpha = 0.9) +
    scale_y_continuous(expand = expand_scale(mult = c(0, 0.05))) +
    theme_minimal_hgrid() +
    theme(legend.position = c(0.1, 0.65)) +
    labs(x = 'Year',
         y = 'Number of hot dogs & buns\nin 10 minutes',
         fill = 'Winner',
         title = "Winner of Nathan's hot dog eating competition,\nmen's division")
```

---

.leftcol[
## Points

Plotting the data points is a good starting point<br>&nbsp;

```{r ref.label='milk_ca_point', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]
--
.rightcol[
## Points + line

Adding lines between the points helps<br>see the overall trend

```{r ref.label='milk_ca_point_line', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]

---

.leftcol[
## Line

Omitting the points emphasizes the overall trend<br>&nbsp;

```{r ref.label='milk_ca_line', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]
--
.rightcol[
## Line + area

Filling area below line further emphasizes the trend,<br>but the y-axis must start at zero

```{r ref.label='milk_ca_line_area', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```

]

---
class: center, middle

### If points are too sparse, a line can be misleading

.leftcol[
```{r ref.label='milk_ca_point_line_sparse1', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]
.rightcol[
```{r ref.label='milk_ca_point_line_sparse2', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]

---

.leftcol[
## Smoothed line

Adding a "smoothed" line shows a modeled representation of the overall trend

```{r ref.label='milk_ca_smooth', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]
--
.rightcol[
## Smoothed line + points

Putting the smoothed line over the data points helps show whether **outliers** are driving the trend line

```{r ref.label='milk_ca_smooth_points', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]

---
class: center, middle

### Bars are useful when emphasizing the **data points**<br>rather than the **slope between them**

.leftcol[
```{r ref.label='hotdog_bar_record', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]
--
.rightcol[
```{r ref.label='hotdog_bar_winner', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]

---
## How to: **Points + line**

.leftcol[.code70[
```{r, eval=FALSE}
ggplot(milk_ca,
    aes(x = year, y = milk_produced)) + #<<
    geom_point(color = 'steelblue', size = 2) + #<<
    geom_line(color = 'steelblue', size = 0.5) + #<<
    theme_half_open(font_size = 18) +
    labs(x = 'Year',
         y = 'Milk produced (billion lbs)',
         title = 'Milk production in California')
```
]]
.rightcol[
```{r ref.label='milk_ca_point_line', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]

---

## How to: **Line + area**

.leftcol[.code70[
```{r, eval=FALSE}
ggplot(milk_ca,
    aes(x = year, y = milk_produced)) +
    geom_line(color = 'steelblue', size = 1) + #<<
    geom_area(fill = 'steelblue', alpha = 0.5) + #<<
    scale_y_continuous(
        expand = expand_scale(mult = c(0, 0.05))) +
    theme_half_open(font_size = 18) +
    labs(x = 'Year',
         y = 'Milk produced (billion lbs)',
         title = 'Milk production in California')
```
]]
.rightcol[
```{r ref.label='milk_ca_line_area', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]

---

## How to: **Smoothed line + points**

.leftcol[.code70[
```{r, eval=FALSE}
ggplot(milk_ca,
    aes(x = year, y = milk_produced)) +
    geom_point(color = 'grey', #<<
               size = 2, #<<
               alpha = 0.9) + #<<
    geom_smooth(color = 'steelblue', #<<
                size = 1, #<<
                se = FALSE) + #<<
    theme_half_open(font_size = 18) +
    labs(x = 'Year',
         y = 'Milk produced (billion lbs)',
         title = 'Milk production in California')
```
]]
.rightcol[
```{r ref.label='milk_ca_smooth_points', echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
```
]

---
class: inverse

## Your turn

.leftcol[

Use the `nasa_global_temps.csv` data to explore ways to visualize the change in average global temperatures.

Consider using:

- points
- lines
- areas
- smoothed lines

]
.rightcol[
```{r, echo=FALSE, fig.height=5, fig.width=6, fig.align='center'}
ggplot(global_temps,
       aes(x = year, y = meanTemp)) +
    geom_point(color = 'steelblue', size = 1.5) +
    theme_half_open() +
    labs(x = 'Year',
         y = 'Temperature anomaly (C)')
```
]
