---
title: "Week 2 In Class Notes"
output: html_document
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
options(
    htmltools.dir.version = FALSE,
    knitr.table.format = "html",
    knitr.kable.NA = '')
knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.retina = 3)
```

# Practice with data types

1) Read in the following data sets:

- `milk_production.csv`
- `lotr_words.csv`

2) For each variable in each data set, note the data type:
 
Categorical | Numerical
------------|------------
Nominal     | Interval
Ordinal     | Ratio

3) Share your results with your neighbor

```{r}
# Write code here
```


# Practice with summary measurements: centrality & variability

1) Read in the following data sets:

- `milk_production.csv`
- `lotr_words.csv`

 2) For each variable in each data set, if possible, summarize its

- _Centrality_
- _Variability_

3) Share your results with your neighbor

```{r}
# Write code here
```


# Practice with visual summaries

1) Read in the following data sets:

- `faithful.csv`
- `marathon.csv`

2) Summarize the following variables using an appropriate chart (bar chart, histogram, and / or boxplot):

- faithful: `eruptions`
- faithful: `waiting`
- marathon: `Age`
- marathon: `State`
- marathon: `Country`
- marathon: `` `Official Time` ``

3) Share what you learned about each variable with your neighbor.

```{r}
# Write code here
```



# Practice with visualizing relationships

1) Read in the following data sets:

- `marathon.csv`
- `wildlife_impacts.csv`

2) Visualize the _relationships_ between the following variables using an appropriate chart (bar plots, scatterplots, and / or box plots):

- marathon: `Age` & `` `Official Time` ``
- marathon: `` `M/F` `` & `` `Official Time` ``
- wildlife_impacts: `state` & `operator`

3) Share what you learned about each variable with your neighbor.

```{r}
# Write code here
```



# Practice doing EDA 

1) Read in the following data set: `data.csv`

2) For each variable, note the data type:

Categorical | Numerical
------------|-----------
Nominal     | Interval
Ordinal     | Ratio

3) For each variable, if possible, summarize its

- _Centrality_
- _Variability_

4) Summarize some of the variables using an appropriate chart:

- Bar chart
- Histogram
- Boxplot

5) Visualize a _relationship_ between two variables using an appropriate chart:

- Bar chart
- Scatterplot
- Boxplot

```{r}
# Write code here
```
